Network Fusion through CDRP Model\\ Decomposition and Assembly

### 2019-12-24 paper/paper.tex
update paper outline
update title and some formulation

@@

%% Title information
\title[]{NO TITLE}         %% [Short Title] is optional;
%% when present, will be used in
%% header instead of Full Title.
%\titlenote{ }             %% \titlenote is optional;
%% can be repeated if necessary;
%% contents suppressed with 'anonymous'
%\subtitle{Subtitle}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
%% can be repeated if necessary;
%% contents suppressed with 'anonymous'

@@

@@

\author{Zhongye Wang}
% \authornote{Supervised by Qinxiang Cao, Shanghai Jiao Tong University, John Hopcroft Center for Computer Science.}          %% \authornote is optional;
%% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
	%\position{Position2b}
	%\department{Department2b}             %% \department is recommended
	\institution{Shanghai Jiao Tong University}           %% \institution is required
	%\streetaddress{Street3b Address2b}
	%\city{City2b}
	%\state{State2b}
	%\postcode{Post-Code2b}
	%\country{Country2b}                   %% \country is recommended
}
\email{wangzhongye1110@sjtu.edu.cn}          %% \email is recommended

@@

\section{Body}
The body \dots

>>>>

\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}

@@

%% Title information
\title[Network Fusion through CDRP Model Decomposition and Assembly]{Network Fusion through CDRP Model\\ Decomposition and Assembly}         %% [Short Title] is optional;
%% when present, will be used in
%% header instead of Full Title.
%\titlenote{ }             %% \titlenote is optional;
%% can be repeated if necessary;
%% contents suppressed with 'anonymous'
%\subtitle{Subtitle}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
%% can be repeated if necessary;
%% contents suppressed with 'anonymous'

@@

\author{Zhongye Wang}
% \authornote{Supervised by Qinxiang Cao, Shanghai Jiao Tong University, John Hopcroft Center for Computer Science.}          %% \authornote is optional;
%% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
	%\position{Position2b}
	%\department{Department2b}             %% \department is recommended
	\institution{Shanghai Jiao Tong University}           %% \institution is required
	%\streetaddress{Street3b Address2b}
	%\city{City2b}
	%\state{State2b}
	%\postcode{Post-Code2b}
	%\country{Country2b}                   %% \country is recommended
}
% \email{wangzhongye1110@sjtu.edu.cn}          %% \email is recommended

@@

@@

\subsection{Our Work}

\section{CDRP Model Decomposition and Clustering}
\subsection{Critical Data Routing Path Model}
\subsection{CDRP Model Clustering}

\section{CDRP Model Assembly}
\subsection{The Assembly Problem}
For a clear formulation, we define the input of a problem instance to have the following components:
\begin{itemize}
	\item $L$ class labels, denoted $\{l_j\}$
	\item $N$ subclasses in total \begin{itemize}
		\item $M$ target subclasses, denoted $\mathcal{A} = \{A_i\}$
		\item $N-M$ dummy subclasses (with irrelevant class labels), denoted $\bar{\mathcal{A}} = \{A_i\}$
	\end{itemize}
	\item $g(A_i) := l_j$ the partial map from $A_i$ to class label $l_j$
	\item $K$ classifiers, denoted $\mathcal{D} = \{d_j\}$
	\item $f(A_i, d_j) := 0, 1$ the classifier certificate that $A_i$ is classified positive in classifier $d_j$
	\item $score(d_j)$ the accuracy(?) of classifier $d_j$
	\item $k$ the maximum number of classifier to use
\end{itemize}

The solution to the instance should contain:
\begin{itemize}
	\item $D \subset \mathcal{D}$ a set of $m$ classifiers \textit{covering} all $M$ target subclasses s.t. $m < k$
	\item $score(D)$ the overall accuracy(?) of the classifier set
\end{itemize}

We define the concept of \textit{covering} as follows.
\begin{definition}
	A set of classifiers covers $M$ target subclasses iff. given any sample, the joint classifier can determine whether it \textit{solely} belongs to \begin{enumerate}
		\item a subset (with consistent labels) of the $M$ target subclasses, or,
		\item the rest dummy subclasses $\bar{\mathcal{A}}$.
	\end{enumerate}
\end{definition}

We start with analyzing the intractability of the problem.
\begin{theorem}
	The assembly problem is an NP problem.
\end{theorem}
\begin{proof}
We prove the theorem by giving a polynomial algorithm for the certificate problem.

Given a certificate $D \subset \mathcal{D}$, we encode each subclass with a binary string $s$ of length $k$, where the $j$-th element for the $i$ subclass is $f(A_i, d_j)$ ($d_j \in D$).
This step takes $O(Nk) = O(NK)$ time.
The algorithm returns $yes$ iff. \begin{enumerate}
	\item No two subclasses in $\mathcal{A}$ share the same encoding but have different labels, and,
	\item No subclass in $\mathcal{A}$ shares the same encoding with any subclass in $\bar{\mathcal{A}}$.
\end{enumerate}
Otherwise, it returns $no$.
This step takes $O(N)$ if we use hash table to record the occurrence of encoded strings.

% TODO: correctness proof
\todo{More proof of the algorithm's correctness}
\end{proof}

\subsection{The Algorithm}

\section{Experiments}
\subsection{CDRP Models of VGGNet and ? trained on CIFAR-100}
\subsection{Fusing VGGNet and ? for Specific Tasks through CDRP Assembly}
